Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-03 talk/dls2014/paper/paper.tex
clarifications

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{\string"page remapping\string".pdf}
  \caption{Page Remapping: (I) after \texttt{mmap()}. (II) remap all pages to
    segment~0, fully shared memory configuration. (III) privatise single
    pages.\label{fig:Page-Remapping}}
\end{figure}

@@

On startup, we reserve a big range of virtual memory with a call to
\lstinline!mmap()! and partition this space into $N+1$ segments. We
want to run $N$ threads in parallel while segment~0 is designated as
the \emph{sharing-segment} that is never assigned to a thread.

The next step involves using \lstinline!remap_file_pages()!, a Linux
system call, to establish the fully-shared configuration.  All pages
of segments $>0$ map to the pages of the sharing-segment.

@@

\bibitem{wayforward14} Remigius Meier, Armin Rigo. 2014. A Way Forward
  in Parallelising Dynamic Languages. Under review in ICOOOLPS'14.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{\string"page remapping\string".pdf}
  \caption{Page Remapping: (I) initial setting. (II) remap all pages to
    segment~0, fully shared memory configuration. (III) privatise single
    pages.\label{fig:Page-Remapping}}
\end{figure}

@@

On startup, we reserve a big range of virtual memory with a call to
\lstinline!mmap()! and partition this space into $N+1$ segments. We
want to run $N$ threads in parallel while segment~0 is designated as
the \emph{sharing-segment} that is never assigned to a thread. The
sharing-segment is essentially read-only except during commit.

The next step involves using \lstinline!remap_file_pages()!, a Linux
system call, to establish the \emph{fully-shared configuration}.  All pages
of segments $>0$ map to the pages of the sharing-segment.

@@

\bibitem{wayforward14} Remigius Meier, Armin Rigo. 2014. A Way Forward
  in Parallelising Dynamic Languages. ICOOOLPS'14.
